### 2024-03-25 manuscript.Rmd
update methods

We used the Fiji distribution of ImageJ2 [@schindelinFiji2012] to digitally visualise X-ray images and counted the number of vertebrae using Cell Counter module. Precloacal and postcloacal vertebrae were distinguished based on vertebral morphology.

Additionally, we quantified the vertebral profile for two representative blindsnake species (*A. grypus* and *A. ligatus*) by measuring the length of each vertebra from the first pre-cloacl vertebra to the last tail vertebra. Following @sherrattMacroevolution2022 we used the 'multipoint tool' in ImageJ2 where landmarks were placed medially along the vertebral column at the anterior limit of the centrum of each vertebra.

## PICK UP HERE $*)#$@

@@

Occurrence data were based on locality records of preserved specimens from museum databases and verified human observations from Atlas of the Living Australia (ALA). We modified some records to reflect the latest taxonomic changes based on updated distribution range and ST's examination of specimens. We discarded records with identical latitude and longitude, and records with uncertain taxonomic identities. In total we retained 3896 verified records representing every species of Australian *Anilios* for our analyses (See data availability statement).

We selected soil bulk density, annual mean temperature, and aridity index as the most biologically relevant data to describe blindsnake niches. 
Soil bulk density measures the penetrability of soil, which is relevant for strictly fossorial reptiles [camaitiMacroecological2022]. Bulk density is calculated by taking the weight of dry soil divided by the total soil volume (g/cm<sup>3</sup>). Values > 1.6 g/cm<sup>3</sup> tend to restrict root growth, while loose soil have densities < 0.5 g/cm<sup>3</sup> [@mckenzieSoil2002]. Mean annual temperature serves as a climate proxy and is commonly used to describe niche for squamate reptiles [@coxEvolutionary2015;@pieEvolution2017;@wiensDiversity2013]. Finally, aridity index reflects precipitation availability over atmospheric water demand and is categorised as follows: hyper arid, < 0.03; arid, 0.03 – 0.2; semi-arid, 0.2-0.5; dry sub-humid, 0.5 – 0.65; humid, >0.65 [@zomerVersion2022]. 
From raster files that contained modelled approximations at the resolution of 3 arc-seconds, we extracted soil bulk density values between 0 — 5cm depth from [CSIRO Soil and Landscape Grid of Australia](https://www.clw.csiro.au/aclep/soilandlandscapegrid/index.html), mean annual temperature from WorldClim v.2 [@fickWorldClim2017], and aridity index from @zomerVersion2022 for each georeferenced record using the "extract" function in the R package `raster` v.3.6-3 [@hijmansRaster2022]. We then calculated the maximum soil bulk density, mean annual temperature, and mean aridity index for each species. Correlation analyses revealed that none of the background environmental variables were strongly correlated (Pearson's *r* < |0.75|).

>>>>

We used the Fiji distribution of ImageJ2 [@schindelinFiji2012] to digitally visualise X-ray images and counted the number of vertebrae using Cell Counter module. Precloacal and postcloacal vertebrae were distinguished based on vertebral morphology. Additionally, we quantified intracolumnar length of each vertebrae for two representative blindsnake species (*A. grypus* and *A. ligatus*). Following @sherrattMacroevolution2022 we used the 'multipoint tool' in ImageJ2 to place landmarks medially along the vertebral column at the anterior limit of the centrum of each vertebra. We then calculated the inter-landmark distances by applying the Pythagorean theorem between sequential landmark coordinates in R. Measurements were repeated three times to acccount for measurement errors.

@@

<!-- NEED TO PUT IN THE CORRECT VALUES HERE -->
We used the Australian blindsnake occurrence records presented in (Tiatragul et al. unpublished). These records were compiled from museum databases and verified human observations from Atlas of the Living Australia (ALA). A total of XXXX records (min = , median = , max = , median per species) representing XX species of Australian *Anilios* for our analyses.

###<!-- PICK UP HERE -->###
We selected soil bulk density, annual mean temperature, and aridity index as the most biologically relevant data to describe blindsnake niches. 
Soil bulk density measures the penetrability of soil, which is relevant for strictly fossorial reptiles [camaitiMacroecological2022]. Bulk density is calculated by taking the weight of dry soil divided by the total soil volume (g/cm<sup>3</sup>). Values > 1.6 g/cm<sup>3</sup> tend to restrict root growth, while loose soil have densities < 0.5 g/cm<sup>3</sup> [@mckenzieSoil2002]. Mean annual temperature serves as a climate proxy and is commonly used to describe niche for squamate reptiles [@coxEvolutionary2015;@pieEvolution2017;@wiensDiversity2013]. Finally, aridity index reflects precipitation availability over atmospheric water demand and is categorised as follows: hyper arid, < 0.03; arid, 0.03 – 0.2; semi-arid, 0.2-0.5; dry sub-humid, 0.5 – 0.65; humid, >0.65 [@zomerVersion2022]. 
From raster files that contained modelled approximations at the resolution of 3 arc-seconds, we extracted soil bulk density values between 0 — 5cm depth from [CSIRO Soil and Landscape Grid of Australia](https://www.clw.csiro.au/aclep/soilandlandscapegrid/index.html), mean annual temperature from WorldClim v.2 [@fickWorldClim2017], and aridity index from @zomerVersion2022 for each georeferenced record using the "extract" function in the R package `raster` v.3.6-3 [@hijmansRaster2022]. We then calculated the maximum soil bulk density, mean annual temperature, and mean aridity index for each species. Correlation analyses revealed that none of the background environmental variables were strongly correlated (Pearson's *r* < |0.75|).
